%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Mid Software Engineer} % Job title
{PagoPa s.p.a.} % Organization
{Milan (Remote)} % Location
{July. 2022 - Now} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Collaborate with external team to design and develop microservices. }
\item { Contributed to maintaining and enhancing the PagoPA eCommerce platform, mainly on autoscaling practices. }
\item { Contributed to maintaining and enhancing Italian citizens' Wallet service. Worked on the migration of 6 millions of wallets. }
\item {Successfully introduced native compilation in Java and Kotlin using GraalVM, resulting in a reduction in resource consumption for microservices. Also working on OpenTelemetry integration on whole systems. }
\item {Passionate about Domain-Driven Design (DDD), focusing on building scalable architectures to handle high volumes of transactions.}
\item { Working with Kubernetes, Kafka, Spring Boot, Quarkus and Azure Cloud }
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Mobile Software Engineer} % Job title
{Sysdata s.p.a.} % Organization
{Bologna} % Location
{May. 2021 - July. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working on Android and Flutter mobile app for various customers}
\item {Became an expert in Flutter hybrid development. Worked on integration between flutter and existing android app}
\item {Working with Kotlin and Dart languages}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}